---
title: "Hoop Analytics Powered by R"
author: "Chris Campbell"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: '3'
    number_sections: true
  pdf_document:
    toc: true
    toc_depth: '3'
always_allow_html: true
---

```{r setup, include=FALSE}
library(nbastatR)
library(ggplot2)
library(dplyr)
library(caret)
library(randomForest)
library(glue)
library(kableExtra)
library(patchwork)
library(devtools)
library(renv)

# Set a global seed for reproducibility
set.seed(123)
```

# Introduction

hooplyticsR, a data-driven project, analyzes basketball player performance using advanced statistical techniques and data visualization from the nbastatR package. It provides in-depth insights into player performance variability and trends by analyzing key metrics like points, rebounds, assists, and fantasy scores. The project aims to create an interactive platform for analyzing basketball data, identifying patterns, and supporting decision-making in player evaluation and fantasy basketball. hooplyticsR makes basketball data more accessible and actionable through statistical analysis and powerful visualizations.

```{r player data input, warning=FALSE, include=FALSE}
# Input the names of the NBA players you want to analyze
players <- c("Stephen Curry", "Jimmy Butler III", "Domantas Sabonis", 
             "Shai Gilgeous-Alexander")

# Get player data from the past 10 seasons
player_data <- game_logs(seasons = c(2015:2025),
                         result_types = "player",
                         Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2))
```

# Player Statistics

This section provides a detailed statistical overview of various basketball players based on their performance across multiple metrics. For each player, we calculate both average values and standard deviations for key performance indicators such as points, rebounds, assists, and fantasy scores. These calculations allow for an in-depth understanding of a player’s consistency and overall impact on the game.

## Key Statistics Included

1. **Games Played**: The total number of games each player participated in.
2. **Average Points**: The player’s average points scored per game.
3. **Average Rebounds**: The average number of rebounds grabbed per game.
4. **Average Assists**: The average number of assists made per game.
5. **Average Points + Rebounds + Assists (PRA)**: A combined measure of points, rebounds, and assists to give a broader view of overall player contribution.
6. **Average 3-Point Field Goals Made**: The average number of successful three-pointers made per game.
7. **Average Steals + Blocks**: A combined statistic for steals and blocks, reflecting a player’s defensive impact.
8. **Average Turnovers**: The average number of turnovers committed per game.
9. **Average Fantasy Score**: A calculated fantasy score based on points, rebounds, assists, steals, blocks, and turnovers.
10. **Standard Deviation (SD) Values**: For each key metric, the standard deviation is provided, indicating how consistent the player is across games.

This summary is generated for each player, providing a clear and concise view of their performance and variability over time. The summary can be used to identify trends, strengths, and areas for improvement, and can be easily included in reports or further analysis.

```{r player stats, echo=FALSE, results='asis'}
# Function to retrieve the average points per game for a list of players
get_avg_player_stats <- function(player_names) {
  # Filter the player data to only include the players in the list
  player_data_filtered <- player_data %>%
    filter(.data$namePlayer %in% player_names)

  # Calculate the average stats for each player
  avg_stats <- player_data_filtered %>%
    group_by(namePlayer) %>%
 summarize(
      games_played = n(), # Number of games played
      # Average Points
      avg_points = round(mean(pts, na.rm = TRUE), 2),
      # Average Rebounds
      avg_rebounds = round(mean(treb, na.rm = TRUE), 2),
      # Average Assists
      avg_assists = round(mean(ast, na.rm = TRUE), 2),
      # Average Points + Rebounds + Assists
      avg_pra = round(mean(pts + treb + ast, na.rm = TRUE), 2),
      # Average 3pt Field Goals Made
      avg_3pm = round(mean(fg3m, na.rm = TRUE), 2),
      # Average Steals + Blocks
      avg_stl_blk = round(mean(stl + blk, na.rm = TRUE), 2),
      # Average Turnovers
      avg_turnovers = round(mean(tov, na.rm = TRUE), 2),
      # Average Fantasy Score
      fantasy_score = round(mean(pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 +
                                   blk * 3 - tov * 1, na.rm = TRUE), 2),
      # Standard Deviation of Points
      sd_points = round(sd(pts, na.rm = TRUE), 2),
      # Standard Deviation of Rebounds
      sd_rebounds = round(sd(treb, na.rm = TRUE), 2),
      # Standard Deviation of Assists
      sd_assists = round(sd(ast, na.rm = TRUE), 2),
      # Standard Deviation of Points + Rebounds + Assists
      sd_pra = round(sd(pts + treb + ast, na.rm = TRUE), 2),
      # Standard Deviation of 3pt Field Goals Made
      sd_3pm = round(sd(fg3m, na.rm = TRUE), 2),
      # Standard Deviation of Steals + Blocks
      sd_stl_blk = round(sd(stl + blk, na.rm = TRUE), 2),
      # Standard Deviation of Turnovers
      sd_turnovers = round(sd(tov, na.rm = TRUE), 2),
      # Standard Deviation of Fantasy Score
      sd_fantasy_score = round(sd(pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 +
                                    blk * 3 - tov * 1, na.rm = TRUE), 2)
    ) %>%
    # Rename the columns for better readability
    rename(
      Player = namePlayer,
      Games_Played = games_played,
      Points = avg_points,
      Rebounds = avg_rebounds,
      Assists = avg_assists,
      Pts_Rebs_Assists = avg_pra,
      Three_Pts_Made = avg_3pm,
      Steal_Blocks = avg_stl_blk,
      Turnovers = avg_turnovers,
      Fantasy_Score = fantasy_score,
      SD_Points = sd_points,
      SD_Rebounds = sd_rebounds,
      SD_Assists = sd_assists,
      SD_Pts_Rebs_Assists = sd_pra,
      SD_Three_Pts_Made = sd_3pm,
      SD_Steal_Blocks= sd_stl_blk,
      SD_Turnovers = sd_turnovers,
      SD_Fantasy_Score = sd_fantasy_score
    )

  return(avg_stats)
}
# Return the average points per game for the list of players
player_stats_df <- data.frame(get_avg_player_stats(players))

## Summary Analysis

# Function to create a summary for each player

generate_player_summary <- function(player_stats_df) {
  summaries <- apply(player_stats_df, 1, function(row) {
    glue::glue(
"### {row['Player']}

<table style='width:100%; border-collapse: collapse;'>
  <tr>
    <td style='vertical-align:top; width:50%; border: 1px solid #ddd; padding: 5px;'>
      <strong>Games Played:</strong> {row['Games_Played']}<br>
      <strong>Average Points:</strong> {row['Points']}<br>
      <strong>Average Rebounds:</strong> {row['Rebounds']}<br>
      <strong>Average Assists:</strong> {row['Assists']}<br>
      <strong>Average PRA:</strong> {row['Pts_Rebs_Assists']}<br>
      <strong>Average 3PM:</strong> {row['Three_Pts_Made']}<br>
      <strong>Average Steals+Blocks:</strong> {row['Steal_Blocks']}<br>
      <strong>Average Turnovers:</strong> {row['Turnovers']}<br>
      <strong>Average Fantasy Score:</strong> {row['Fantasy_Score']}<br>
    </td>
    <td style='vertical-align:top; width:50%; border: 1px solid #ddd; padding: 5px;'>
      <strong>Consistency (Standard Deviation):</strong><br>
      <strong>Points:</strong> {row['SD_Points']}<br>
      <strong>Rebounds:</strong> {row['SD_Rebounds']}<br>
      <strong>Assists:</strong> {row['SD_Assists']}<br>
      <strong>PRA:</strong> {row['SD_Pts_Rebs_Assists']}<br>
      <strong>3PM:</strong> {row['SD_Three_Pts_Made']}<br>
      <strong>Steals+Blocks:</strong> {row['SD_Steal_Blocks']}<br>
      <strong>Turnovers:</strong> {row['SD_Turnovers']}<br>
      <strong>Fantasy Score:</strong> {row['SD_Fantasy_Score']}<br>
    </td>
  </tr>
</table>

<p><em>The lower the standard deviation (SD), the more consistent the player is across games. A high SD indicates variability, suggesting the player's performance is less predictable.</em></p>
<p><em>For instance, a low SD in points means the player typically scores within a narrow range, while a high SD might indicate fluctuating performance.</em></p>

----
"
    )
  })
  
  return(paste(summaries, collapse = "\n\n"))
}

# Show the player summary
cat(generate_player_summary(player_stats_df))

```
## Player Performance Table

The following table summarizes each player's performance across key metrics, allowing for easy comparison. It includes averages for essential statistics such as points, rebounds, assists, fantasy scores, and more.

### Key Metrics
- **Games Played**: Number of games the player participated in.
- **Average Points**: The player's average points scored.
- **Average Rebounds**: The player's average rebounds.
- **Average Assists**: The player's average assists.
- **Average PRA (Points + Rebounds + Assists)**: The combined average of points, rebounds, and assists.
- **Average 3PM**: The average number of three-pointers made.
- **Average Steals + Blocks**: The combined average of steals and blocks.
- **Average Turnovers**: The average number of turnovers committed.
- **Average Fantasy Score**: The player's average fantasy score.

```{r player performance table, echo=FALSE}
# Remove SD_* columns
player_stats_df_no_sd <- player_stats_df %>%
  select(-starts_with("SD_"))


generate_player_summary_table <- function(player_stats_df_no_sd) {
  # Renaming columns for better readability
  colnames(player_stats_df_no_sd) <- c(
    "Player",
    "Games Played",
    "Average Points",
    "Average Rebounds",
    "Average Assists",
    "Average PRA (Pts + Rebs + Assists)",
    "Average 3PM",
    "Average Steals + Blocks",
    "Average Turnovers",
    "Average Fantasy Score"
  )

  # Create the kable
  player_table <- player_stats_df_no_sd %>%
    kable("html", escape = FALSE,
          caption = "Player Performance Breakdown") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = F) %>%
    scroll_box(width = "100%", height = "400px") # Make the kable scrollable

  return(player_table)
}

# Create the summary table
player_summary_table <- generate_player_summary_table(player_stats_df_no_sd)

# Display the table
player_summary_table
```

# Player Performance Visualizations

This section uses visualizations to highlight key player performance statistics and their variability. It explores the distribution and consistency of metrics like scoring, rebounds, assists, three-pointers, turnovers, and fantasy scores. Examining the overall distribution provides insights into player consistency and overall contributions. The visualizations reveal trends and patterns, helping identify more consistent players and aid data-driven decision-making.

## Total Points

```{r plot 1, echo=FALSE}
# Total Points Distribution Visualization
p1 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = pts, fill = namePlayer)) +
  geom_histogram(binwidth = 5, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Points Distribution",
       x = "Points",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p1
```

## Total Rebounds

```{r plot 2, echo=FALSE}
# Total Rebounds Distribution Visualization
p2 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = treb, fill = namePlayer)) +
  geom_histogram(binwidth = 2, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Rebounds",
       x = "Total Rebounds",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p2
```

## Total Assists

```{r plot 3, echo=FALSE}
# Total Assists Distribution Visualization
p3 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = ast, fill = namePlayer)) +
  geom_histogram(binwidth = 2, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Assists",
       x = "Total Assists",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p3
```

## Total Points + Rebounds + Assists

```{r plot 4, echo=FALSE}
# Total Points + Rebounds + Assists Distribution Visualization
p4 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = pts + treb + ast, fill = namePlayer)) +
  geom_histogram(binwidth = 5, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Points + Rebounds + Assists",
       x = "Total Points + Rebounds + Assists",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p4
```

## Total Three-Pointers Made

```{r plot 5, echo=FALSE}
# Total Three-Pointers Made Distribution Visualization
p5 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = fg3m, fill = namePlayer)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Three-Pointers Made",
       x = "Total Three-Pointers Made",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p5
```

## Total Steals + Blocks

```{r plot 6, echo=FALSE}
# Total Steals + Blocks Distribution Visualization
p6 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = stl + blk, fill = namePlayer)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Steals + Blocks",
       x = "Total Steals + Blocks",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p6
```

## Total Turnovers

```{r plot 7, echo=FALSE}
# Total Turnovers Distribution Visualization
p7 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = tov, fill = namePlayer)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Turnovers",
       x = "Total Turnovers",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p7
```

## Total Fantasy Score

```{r plot 8, echo=FALSE}
# Total Fantasy Score Distribution Visualization
p8 <- player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 + blk * 3 - tov * 1, fill = namePlayer)) +
  geom_histogram(binwidth = 5, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Fantasy Score",
       x = "Total Fantasy Score",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p8
```


```{r ml models, include=FALSE}
train_knn_models <- function(player_data, player_names) {
  # Filter and prepare the data: select players and add derived columns
  player_data_filtered <- player_data %>%
    filter(namePlayer %in% player_names) %>%
    mutate(
      points = pts,                 # clarity alias
      rebounds = treb,              # clarity alias
      assists = ast,                # clarity alias
      total_pra = pts + treb + ast, # composite stat
      threepm = fg3m,               # 3-point makes
      stl_blk = stl + blk,          # combined defensive stats
      turnovers = tov,              # turnovers as is
      fantasy_score = fpts          # fantasy points
    ) %>%
    na.omit()
  
  # Split data into training and test sets (80/20 split)
  train_index <- createDataPartition(player_data_filtered$fpts, p = 0.8, list = FALSE)
  train_data <- player_data_filtered[train_index, ]
  test_data <- player_data_filtered[-train_index, ]
  
  # Define control settings for cross-validation
  control <- trainControl(
    method = "repeatedcv",
    number = 5,         # 5-fold CV for speed
    repeats = 2,        # 2 repeats
    summaryFunction = defaultSummary,
    savePredictions = "final",
    returnResamp = "all",
    search = "grid",
    verboseIter = TRUE
  )
  
  # Define a tuning grid for kNN (for models that use kNN)
  knn_grid <- expand.grid(k = seq(3, 21, by = 1))
  
  # Train models:
  models <- list(
    # Points model: response pts, predictors based on shooting metrics and minutes
    points_model = train(pts ~ fgm + fg3m + ftm + minutes + pctFG + pctFT, 
                         data = train_data, 
                         method = "knn", 
                         tuneGrid = knn_grid,
                         preProcess = c("center", "scale"),
                         trControl = control),
    
    # Rebounds model: response treb, predictors: offensive and defensive rebounds, minutes
    rebounds_model = train(treb ~ oreb + dreb + minutes, 
                           data = train_data, 
                           method = "knn", 
                           tuneGrid = knn_grid,
                           preProcess = c("center", "scale"),
                           trControl = control),
    
    # Assists model: use random forest for improved performance
    assists_model = train(ast ~ minutes + pts + plusminus + fga, 
                          data = train_data, 
                          method = "rf", 
                          preProcess = c("center", "scale"),
                          trControl = control),
    
    # Total PRA model: response total_pra, predictors: pts, treb, ast, minutes, plusminus
    total_pra_model = train(total_pra ~ pts + treb + ast + minutes + plusminus, 
                            data = train_data, 
                            method = "knn", 
                            tuneGrid = knn_grid,
                            preProcess = c("center", "scale"),
                            trControl = control),
    
    # ThreePM model: response fg3m, predictors: fg3a, minutes, pctFG3
    threepm_model = train(fg3m ~ fg3a + minutes + pctFG3, 
                          data = train_data, 
                          method = "knn", 
                          tuneGrid = knn_grid,
                          preProcess = c("center", "scale"),
                          trControl = control),
    
    # Stl+Blk model: response stl_blk, predictors: minutes and plusminus
    stl_blk_model = train(stl_blk ~ minutes + plusminus, 
                          data = train_data, 
                          method = "knn", 
                          tuneGrid = knn_grid,
                          preProcess = c("center", "scale"),
                          trControl = control),
    
    # Turnovers model: response tov, predictors: minutes, fga, ast
    turnovers_model = train(tov ~ minutes + fga + ast, 
                            data = train_data, 
                            method = "knn", 
                            tuneGrid = knn_grid,
                            preProcess = c("center", "scale"),
                            trControl = control),
    
    # Fantasy Score model: use random forest for improved performance
    fantasy_score_model = train(fpts ~ pts + treb + ast + stl + blk + tov + minutes + plusminus, 
                                data = train_data, 
                                method = "rf", 
                                preProcess = c("center", "scale"),
                                trControl = control)
  )
  
  return(list(models = models, train_data = train_data, test_data = test_data))
}

```


```{r train models, include=FALSE}
# Train the models using player_data and players list
model_data <- train_knn_models(player_data, players)
models <- model_data$models
train_data <- model_data$train_data
test_data <- model_data$test_data

```


```{r evaluate models, include=FALSE}
# Function to calculate RMSE
calculate_rmse <- function(predictions, actual_values) {
  sqrt(mean((predictions - actual_values)^2, na.rm = TRUE))
}

# Function to evaluate models and get predictions
evaluate_knn_models <- function(models, test_data) {
  predictions <- list()
  
  # Outcome mapping: model name -> test_data response column
  outcome_mapping <- list(
    points_model        = "pts",
    rebounds_model      = "treb",
    assists_model       = "ast",
    total_pra_model     = "total_pra",
    threepm_model       = "fg3m",
    stl_blk_model       = "stl_blk",
    turnovers_model     = "tov",
    fantasy_score_model = "fpts"
  )
  
  for (model_name in names(models)) {
    model <- models[[model_name]]
    
    # Get predictor variables used in the model (excluding .outcome if present)
    model_vars <- setdiff(colnames(model$trainingData), ".outcome")
    
    # Ensure test data contains all these predictors
    missing_vars <- setdiff(model_vars, colnames(test_data))
    if (length(missing_vars) > 0) {
      stop(paste("Test data is missing the following variables:", paste(missing_vars, collapse = ", ")))
    }
    
    # Subset test data to just the predictor variables
    test_data_with_predictors <- test_data[, model_vars, drop = FALSE]
    
    # Make predictions
    preds <- predict(model, test_data_with_predictors)
    predictions[[model_name]] <- preds
  }
  
  # Compute RMSE for each model
  rmse_results <- list()
  for (model_name in names(predictions)) {
    outcome_col <- outcome_mapping[[model_name]]
    actual_values <- test_data[[outcome_col]]
    rmse_results[[model_name]] <- calculate_rmse(predictions[[model_name]], actual_values)
  }
  
  return(list(predictions = predictions, rmse = rmse_results))
}

# Evaluate the models
results <- evaluate_knn_models(models, test_data)
predictions <- results$predictions
print(results$rmse)

```

# Predictions

In this section, we explore machine learning to predict basketball player performance using historical data. We aim to forecast key statistics like points, rebounds, assists, and fantasy scores with precision. These predictions provide valuable insights for fantasy basketball decisions, player evaluation, and team strategies. Whether drafting or analyzing game performance, our data-driven predictions give you a competitive edge.

```{r model predictions, echo=FALSE, results='asis'}
make_fantasy_decisions_by_model <- function(predictions, test_data, 
                                              player_projections = NULL, 
                                              player_5_game_averages = NULL, 
                                              confidence_margin = 0.1, 
                                              weight_model = 0.5,       # Weight for model difference
                                              weight_5_game_avg = 0.2) {  # Weight for 5-game average
  results_by_player <- list()

  for (i in 1:nrow(test_data)) {
    player_name <- test_data$namePlayer[i]
    best_prediction <- -Inf
    best_model <- NULL
    best_decision <- NULL
    all_predictions <- list()

    for (model_name in names(predictions)) {
      prediction <- as.numeric(predictions[[model_name]][i])
      
      # Get projection: if available in player_projections, else use mean
      projection <- if (!is.null(player_projections) && 
                        player_name %in% names(player_projections) && 
                        model_name %in% names(player_projections[[player_name]])) {
        as.numeric(player_projections[[player_name]][[model_name]])
      } else {
        as.numeric(mean(predictions[[model_name]], na.rm = TRUE))
      }
      
      # If 5-game averages available, compute weighted threshold
      if (!is.null(player_5_game_averages) && 
          player_name %in% names(player_5_game_averages) && 
          model_name %in% names(player_5_game_averages[[player_name]])) {
        five_game_average <- as.numeric(player_5_game_averages[[player_name]][[model_name]])
        weighted_threshold <- (weight_5_game_avg * five_game_average) + ((1 - weight_5_game_avg) * projection)
      } else {
        five_game_average <- NA
        weighted_threshold <- projection
      }
      
      # New threshold calculation: adjust projection by difference scaled by weight_model
      final_threshold <- projection + weight_model * (weighted_threshold - projection)
      adjusted_threshold <- final_threshold * (1 + confidence_margin)
      
      decision <- if (prediction > adjusted_threshold) "More" else "Less"
      
      if (prediction > best_prediction) {
        best_prediction <- prediction
        best_model <- model_name
        best_decision <- decision
      }
      
      all_predictions[[model_name]] <- list(
        model = model_name,
        prediction = round(prediction, 2),
        projection = round(projection, 2),
        weighted_threshold = round(weighted_threshold, 2),
        final_threshold = round(final_threshold, 2),
        adjusted_threshold = round(adjusted_threshold, 2),
        decision = decision,
        five_game_average = round(five_game_average, 2)
      )
    }
    
    results_by_player[[player_name]] <- list(
      player_name = player_name,
      best_prediction = round(best_prediction, 2),
      best_model = best_model,
      best_decision = best_decision,
      all_predictions = all_predictions
    )
  }
  
  # Sort results by player name alphabetically
  sorted_player_names <- sort(names(results_by_player))
  sorted_results <- results_by_player[sorted_player_names]
  
  # Print results for each player
  for (player_name in sorted_player_names) {
    result <- sorted_results[[player_name]]
    player_result <- paste0(
      "Player: ", result$player_name, " | Best Prediction: ", result$best_prediction, 
      " | Best Model: ", result$best_model, " | Decision: ", result$best_decision, "\n"
    )
    
    for (prediction in result$all_predictions) {
      player_result <- paste0(
        player_result,
        "Model: ", prediction$model, 
        " | Prediction: ", prediction$prediction, 
        " | Projection: ", prediction$projection, 
        " | Threshold: ", prediction$final_threshold, 
        " | Adjusted Threshold: ", prediction$adjusted_threshold, 
        " | 5-Game Avg: ", prediction$five_game_average, 
        " | Decision: ", prediction$decision, "\n"
      )
    }
    # cat(player_result, "\n")
  }
  
  return(sorted_results)
}


# Player-specific projections (numeric values)

player_projections <- list(
  "Shai Gilgeous-Alexander" = list(
    points_model = 31.5,
    fantasy_score_model = 50.5
  ),
  "Stephen Curry" = list(
    points_model = 24.5,
    total_pra_model = 35,
    fantasy_score_model = 39
  ),
  "Domantas Sabonis" = list(
    rebounds_model = 11.5,
    fantasy_score_model = 46
  ),
  "Jimmy Butler III" = list(
    points_model = 19.5,
    stl_blk_model = 1.5,
    fantasy_score_model = 38.5
  )
)

# Player 5-game averages (numeric values)
player_5_game_averages <- list(
  "Shai Gilgeous-Alexander" = list(
    points_model = 34.00,
    fantasy_score_model = 53.52
  ),
  "Stephen Curry" = list(
    points_model = 33.20,
    total_pra_model = 43.60,
    fantasy_score_model = 47.62
  ),
  "Domantas Sabonis" = list(
    rebounds_model = 15.00,
    fantasy_score_model = 42.20
  ),
  "Jimmy Butler III" = list(
    points_model = 17.40,
    stl_blk_model = 1.80,
    fantasy_score_model = 37.48
  )
)

# Generate fantasy decisions
results <- make_fantasy_decisions_by_model(predictions, test_data, player_projections, player_5_game_averages)

# Create a summary table for each player with plain text captions and scrollable tables
player_tables <- lapply(results, function(player) {
  # Convert the nested 'all_predictions' list into a data frame
  df <- do.call(rbind, lapply(player$all_predictions, function(pred) {
    data.frame(
      Prediction = pred$prediction,
      Projection = pred$projection,
      Threshold = pred$final_threshold,
      Adjusted_Threshold = pred$adjusted_threshold,
      Five_Game_Avg = pred$five_game_average,
      Decision = pred$decision,
      stringsAsFactors = FALSE
    )
  }))
  
  # Creates a caption that includes the player's name and key details
  caption_text <- paste("Player:", player$player_name, 
                        "| Best Prediction:", player$best_prediction, 
                        "| Best Model:", player$best_model, 
                        "| Decision:", player$best_decision)
  
  list(name = player$player_name, caption = caption_text, table = df)
})

# Format the kable tables for each player
for (pt in player_tables) {
  # Print player's name as a subheading
  cat("##", pt$name, "\n\n")
  print(
    kable(pt$table, format = "html", escape = FALSE, align = "c", caption = pt$caption) %>% 
      kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
      scroll_box(width = "100%", height = "300px")
  )
  cat("\n\n")
}


```
