---
title: "Hoop Analytics Powered by R"
author: "Chris Campbell"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: '3'
    number_sections: true
  pdf_document:
    toc: true
    toc_depth: '3'
always_allow_html: true
---

```{r setup, include=FALSE}
library(nbastatR)
library(ggplot2)
library(lintr)
library(dplyr)
library(caret)
library(randomForest)
library(glue)
library(kableExtra)
```

# Introduction

hooplyticsR, a data-driven project, analyzes basketball player performance using advanced statistical techniques and data visualization from the nbastatR package. It provides in-depth insights into player performance variability and trends by analyzing key metrics like points, rebounds, assists, and fantasy scores. The project aims to create an interactive platform for analyzing basketball data, identifying patterns, and supporting decision-making in player evaluation and fantasy basketball. hooplyticsR makes basketball data more accessible and actionable through statistical analysis and powerful visualizations.

```{r warning=FALSE, include=FALSE}
# NBA Player Data
# A dynamic list of NBA players
players <- c("Kevin Durant", "Joel Embiid",
             "Jalen Brunson", "Donovan Mitchell")

# Get player data for the past three seasons
player_data <- game_logs(seasons = c(2015:2025),
                         result_types = "player",
                         Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 2))
```

# Player Statistics

This section provides a detailed statistical overview of various basketball players based on their performance across multiple metrics. For each player, we calculate both average values and standard deviations for key performance indicators such as points, rebounds, assists, and fantasy scores. These calculations allow for an in-depth understanding of a player’s consistency and overall impact on the game.

### Key Statistics Included:

1. **Games Played**: The total number of games each player participated in.
2. **Average Points**: The player’s average points scored per game.
3. **Average Rebounds**: The average number of rebounds grabbed per game.
4. **Average Assists**: The average number of assists made per game.
5. **Average Points + Rebounds + Assists (PRA)**: A combined measure of points, rebounds, and assists to give a broader view of overall player contribution.
6. **Average 3-Point Field Goals Made**: The average number of successful three-pointers made per game.
7. **Average Steals + Blocks**: A combined statistic for steals and blocks, reflecting a player’s defensive impact.
8. **Average Turnovers**: The average number of turnovers committed per game.
9. **Average Fantasy Score**: A calculated fantasy score based on points, rebounds, assists, steals, blocks, and turnovers.
10. **Standard Deviation (SD) Values**: For each key metric, the standard deviation is provided, indicating how consistent the player is across games.

This summary is generated for each player, providing a clear and concise view of their performance and variability over time. The summary can be used to identify trends, strengths, and areas for improvement, and can be easily included in reports or further analysis.

```{r echo=FALSE}
# Function to retrieve the average points per game for a list of players
get_avg_player_stats <- function(player_names) {
  # Filter the player data to only include the players in the list
  player_data_filtered <- player_data %>%
    filter(.data$namePlayer %in% player_names)

  # Calculate the average stats for each player
  avg_stats <- player_data_filtered %>%
    group_by(namePlayer) %>%
 summarize(
      games_played = n(), # Number of games played
      # Average Points
      avg_points = round(mean(pts, na.rm = TRUE), 2),
      # Average Rebounds
      avg_rebounds = round(mean(treb, na.rm = TRUE), 2),
      # Average Assists
      avg_assists = round(mean(ast, na.rm = TRUE), 2),
      # Average Points + Rebounds + Assists
      avg_pra = round(mean(pts + treb + ast, na.rm = TRUE), 2),
      # Average 3pt Field Goals Made
      avg_3pm = round(mean(fg3m, na.rm = TRUE), 2),
      # Average Steals + Blocks
      avg_stl_blk = round(mean(stl + blk, na.rm = TRUE), 2),
      # Average Turnovers
      avg_turnovers = round(mean(tov, na.rm = TRUE), 2),
      # Average Fantasy Score
      fantasy_score = round(mean(pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 +
                                   blk * 3 - tov * 1, na.rm = TRUE), 2),
      # Standard Deviation of Points
      sd_points = round(sd(pts, na.rm = TRUE), 2),
      # Standard Deviation of Rebounds
      sd_rebounds = round(sd(treb, na.rm = TRUE), 2),
      # Standard Deviation of Assists
      sd_assists = round(sd(ast, na.rm = TRUE), 2),
      # Standard Deviation of Points + Rebounds + Assists
      sd_pra = round(sd(pts + treb + ast, na.rm = TRUE), 2),
      # Standard Deviation of 3pt Field Goals Made
      sd_3pm = round(sd(fg3m, na.rm = TRUE), 2),
      # Standard Deviation of Steals + Blocks
      sd_stl_blk = round(sd(stl + blk, na.rm = TRUE), 2),
      # Standard Deviation of Turnovers
      sd_turnovers = round(sd(tov, na.rm = TRUE), 2),
      # Standard Deviation of Fantasy Score
      sd_fantasy_score = round(sd(pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 +
                                    blk * 3 - tov * 1, na.rm = TRUE), 2)
    ) %>%
    # Rename the columns for better readability
    rename(
      Player = namePlayer,
      Games_Played = games_played,
      Points = avg_points,
      Rebounds = avg_rebounds,
      Assists = avg_assists,
      Pts_Rebs_Assists = avg_pra,
      Three_Pts_Made = avg_3pm,
      Steal_Blocks = avg_stl_blk,
      Turnovers = avg_turnovers,
      Fantasy_Score = fantasy_score,
      SD_Points = sd_points,
      SD_Rebounds = sd_rebounds,
      SD_Assists = sd_assists,
      SD_Pts_Rebs_Assists = sd_pra,
      SD_Three_Pts_Made = sd_3pm,
      SD_Steal_Blocks= sd_stl_blk,
      SD_Turnovers = sd_turnovers,
      SD_Fantasy_Score = sd_fantasy_score
    )

  return(avg_stats)
}
# Return the average points per game for the list of players
player_stats_df <- data.frame(get_avg_player_stats(players))

## Summary Analysis

# Function to create a summary for each player

generate_player_summary <- function(player_stats_df) {
  summaries <- apply(player_stats_df, 1, function(row) {
    glue("
      ### **{row['Player']}**

      **Games Played:** {row['Games_Played']}

      **Average Points:** {row['Points']}
      **Average Rebounds:** {row['Rebounds']}
      **Average Assists:** {row['Assists']}
      **Average Points + Rebounds + Assists (PRA):** {row['Pts_Rebs_Assists']}

      **Average 3-Point Field Goals Made:** {row['Three_Pts_Made']}
      **Average Steals + Blocks:** {row['Steal_Blocks']}
      **Average Turnovers:** {row['Turnovers']}
      **Average Fantasy Score:** {row['Fantasy_Score']}

      **Consistency (Standard Deviation):**
      - **Points:** {row['SD_Points']}
      - **Rebounds:** {row['SD_Rebounds']}
      - **Assists:** {row['SD_Assists']}
      - **PRA (Points + Rebounds + Assists):** {row['SD_Pts_Rebs_Assists']}
      - **3-Point Field Goals Made:** {row['SD_Three_Pts_Made']}
      - **Steals + Blocks:** {row['SD_Steal_Blocks']}
      - **Turnovers:** {row['SD_Turnovers']}
      - **Fantasy Score:** {row['SD_Fantasy_Score']}

      *The lower the standard deviation (SD), the more consistent the player is across games. A high SD indicates variability, suggesting the player's performance is less predictable. For instance, a low SD in points means the player typically scores within a narrow range, while a high SD might indicate fluctuating performance.*

      ----
    ")
  })

  return(paste(summaries, collapse = "\n"))
}

# Call the function to get the summary output
cat(generate_player_summary(player_stats_df))
```
## Player Performance Table

The following table summarizes each player's performance across key metrics, allowing for easy comparison. It includes averages for essential statistics such as points, rebounds, assists, fantasy scores, and more.

### Key Metrics Included:
- **Games Played**: Number of games the player participated in.
- **Average Points**: The player's average points scored.
- **Average Rebounds**: The player's average rebounds.
- **Average Assists**: The player's average assists.
- **Average PRA (Points + Rebounds + Assists)**: The combined average of points, rebounds, and assists.
- **Average 3PM**: The average number of three-pointers made.
- **Average Steals + Blocks**: The combined average of steals and blocks.
- **Average Turnovers**: The average number of turnovers committed.
- **Average Fantasy Score**: The player's average fantasy score.

```{r echo=FALSE}
# Remove SD_* columns
player_stats_df_no_sd <- player_stats_df %>%
  select(-starts_with("SD_"))


generate_player_summary_table <- function(player_stats_df_no_sd) {
  # Renaming columns for better readability
  colnames(player_stats_df_no_sd) <- c(
    "Player",
    "Games Played",
    "Average Points",
    "Average Rebounds",
    "Average Assists",
    "Average PRA (Pts + Rebs + Assists)",
    "Average 3PM",
    "Average Steals + Blocks",
    "Average Turnovers",
    "Average Fantasy Score"
  )

  # Create the kable
  player_table <- player_stats_df_no_sd %>%
    kable("html", escape = FALSE,
          caption = "Player Performance Breakdown") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = F) %>%
    scroll_box(width = "100%", height = "400px") # Make the kable scrollable

  return(player_table)
}

# Create the summary table
player_summary_table <- generate_player_summary_table(player_stats_df_no_sd)

# Display the table
player_summary_table
```

# Data Visualization

This section uses visualizations to highlight key player performance statistics and their variability. It explores the distribution and consistency of metrics like scoring, rebounds, assists, three-pointers, turnovers, and fantasy scores. Examining the overall distribution and standard deviation provides insights into player consistency and overall contributions. The visualizations reveal trends and patterns, helping identify more consistent players and aid data-driven decision-making.

## Total Points Distribution

```{r echo=FALSE}
# Total Points Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = pts, fill = namePlayer)) +
  geom_histogram(binwidth = 5, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Points Distribution",
       x = "Points",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Points

```{r echo=FALSE}
# Standard Deviation of Points Visualization
player_stats_df %>%
  arrange(desc(SD_Points)) %>%
  ggplot(aes(x = reorder(Player, SD_Points), y = SD_Points, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Points",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

```

## Total Rebounds Distribution

```{r echo=FALSE}
# Total Rebounds Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = treb, fill = namePlayer)) +
  geom_histogram(binwidth = 2, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Rebounds Distribution",
       x = "Total Rebounds",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Rebounds

```{r echo=FALSE}
# Standard Deviation of Rebounds Visualization
player_stats_df %>%
  arrange(desc(SD_Rebounds)) %>%
  ggplot(aes(x = reorder(Player, SD_Rebounds), y = SD_Rebounds, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Rebounds",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

## Total Assists Distribution

```{r echo=FALSE}
# Total Assists Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = ast, fill = namePlayer)) +
  geom_histogram(binwidth = 2, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Assists Distribution",
       x = "Total Assists",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Assists

```{r echo=FALSE}
# Standard Deviation of Assists Visualization
player_stats_df %>%
  arrange(desc(SD_Assists)) %>%
  ggplot(aes(x = reorder(Player, SD_Assists), y = SD_Assists, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Assists",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

## Total Points + Rebounds + Assists Distribution

```{r echo=FALSE}
# Total Points + Rebounds + Assists Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = pts + treb + ast, fill = namePlayer)) +
  geom_histogram(binwidth = 5, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Points + Rebounds + Assists Distribution",
       x = "Total Points + Rebounds + Assists",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Points + Rebounds + Assists

```{r echo=FALSE}
# Standard Deviation of Points + Rebounds + Assists Visualization
player_stats_df %>%
  arrange(desc(SD_Pts_Rebs_Assists)) %>%
  ggplot(aes(x = reorder(Player, SD_Pts_Rebs_Assists), y = SD_Pts_Rebs_Assists, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Points + Rebounds + Assists",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

## Total Three-Pointers Made Distribution

```{r echo=FALSE}
# Total Three-Pointers Made Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = fg3m, fill = namePlayer)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Three-Pointers Made Distribution",
       x = "Total Three-Pointers Made",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Three-Pointers Made

```{r echo=FALSE}
# Standard Deviation of Three-Pointers Made Visualization
player_stats_df %>%
  arrange(desc(SD_Three_Pts_Made)) %>%
  ggplot(aes(x = reorder(Player, SD_Three_Pts_Made), y = SD_Three_Pts_Made, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Three-Pointers Made",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

## Total Steals + Blocks Distribution

```{r echo=FALSE}
# Total Steals + Blocks Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = stl + blk, fill = namePlayer)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Steals + Blocks Distribution",
       x = "Total Steals + Blocks",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Steals + Blocks

```{r echo=FALSE}
# Standard Deviation of Steals + Blocks Visualization
player_stats_df %>%
  arrange(desc(SD_Steal_Blocks)) %>%
  ggplot(aes(x = reorder(Player, SD_Steal_Blocks), y = SD_Steal_Blocks, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Steals + Blocks",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

## Total Turnovers Distribution

```{r echo=FALSE}
# Total Turnovers Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = tov, fill = namePlayer)) +
  geom_histogram(binwidth = 1, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Turnovers Distribution",
       x = "Total Turnovers",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Turnovers

```{r echo=FALSE}
# Standard Deviation of Turnovers Visualization
player_stats_df %>%
  arrange(desc(SD_Turnovers)) %>%
  ggplot(aes(x = reorder(Player, SD_Turnovers), y = SD_Turnovers, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Turnovers",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

## Total Fantasy Score Distribution

```{r echo=FALSE}
# Total Fantasy Score Distribution Visualization
player_data %>%
  filter(namePlayer %in% players) %>%
  ggplot(aes(x = pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 + blk * 3 - tov * 1, fill = namePlayer)) +
  geom_histogram(binwidth = 5, position = "dodge", color = "black") +
  facet_wrap(~namePlayer, scales = "free_y", strip.position = "bottom",
             axis.labels = "all_x") +
  labs(title = "Total Fantasy Score Distribution",
       x = "Total Fantasy Score",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Standard Deviation of Fantasy Score

```{r echo=FALSE}
# Standard Deviation of Fantasy Score Visualization
player_stats_df %>%
  arrange(desc(SD_Fantasy_Score)) %>%
  ggplot(aes(x = reorder(Player, SD_Fantasy_Score), y = SD_Fantasy_Score, fill = Player)) +
  geom_bar(stat = "identity") +
  labs(title = "Standard Deviation of Fantasy Score",
       x = "Player",
       y = "Standard Deviation",
       caption = "High SD = Inconsistent Performance,
       Low SD = Consistent Performance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")
```

```{r include=FALSE}
# Machine Learning

# Function to train Random Forest models for betting categories (PrizePicks)
train_rf_models <- function(player_data, player_names) {
  # Filter the player data to only include the players in the list
  player_data_filtered <- player_data %>%
    filter(namePlayer %in% player_names) %>%
    mutate(
      points = pts,
      rebounds = treb,
      assists = ast,
      total_pra = pts + treb + ast,
      threepm = fg3m,
      stl_blk = stl + blk,
      turnovers = tov,
      fantasy_score = pts * 1 + treb * 1.2 + ast * 1.5 + stl * 3 + blk * 3 - tov * 1
    )

  # Remove rows with missing data
  player_data_filtered <- na.omit(player_data_filtered)

  # Split data into training and testing sets
  set.seed(123)
  train_index <- createDataPartition(player_data_filtered$pts, p = 0.8, list = FALSE)
  train_data <- player_data_filtered[train_index, ]
  test_data <- player_data_filtered[-train_index, ]

  # Train models for betting categories
  models <- list(
    points_model = randomForest(pts ~ treb + ast + stl + blk + tov, data = train_data),
    rebounds_model = randomForest(treb ~ pts + ast + stl + blk + tov, data = train_data),
    assists_model = randomForest(ast ~ pts + treb + stl + blk + tov, data = train_data),
    total_pra_model = randomForest(total_pra ~ pts + treb + ast + stl + blk + tov, data = train_data),
    threepm_model = randomForest(fg3m ~ pts + treb + ast + stl + blk + tov, data = train_data),
    stl_blk_model = randomForest(stl_blk ~ pts + treb + ast + blk + tov, data = train_data),
    turnovers_model = randomForest(tov ~ pts + treb + ast + stl + blk, data = train_data),
    fantasy_score_model = randomForest(fantasy_score ~ pts + treb + ast + stl + blk + tov, data = train_data)
  )

  return(list(models = models, test_data = test_data))
}
```


```{r include=FALSE}
# Train Models

rf_model_data <- train_rf_models(player_data, players)
models <- rf_model_data$models
test_data <- rf_model_data$test_data
```


```{r include=FALSE}
# Evaluate Models

# Function to evaluate models and get predictions
evaluate_rf_models <- function(models, test_data) {
  predictions <- list()

  # Evaluate and get predictions for each model
  for (model_name in names(models)) {
    model <- models[[model_name]]

    # Get the predictor variables used in the model
    model_vars <- all.vars(model$call$formula)[-1]  # All vars used for prediction (excluding the target)

    # Ensure that all predictor variables are in the test data
    missing_vars <- setdiff(model_vars, colnames(test_data))
    if (length(missing_vars) > 0) {
      stop(paste("Test data is missing the following variables:", paste(missing_vars, collapse = ", ")))
    }

    # Subset test data to only include the predictor variables
    test_data_with_predictors <- test_data[, model_vars, drop = FALSE]

    # Make predictions for the model
    predictions[[model_name]] <- predict(model, test_data_with_predictors)
  }

  return(predictions)
}

# Evaluate models and get predictions
predictions <- evaluate_rf_models(models, test_data)
```

# **Predictions**

In this section, we explore machine learning to predict basketball player performance using historical data. We aim to forecast key statistics like points, rebounds, assists, and fantasy scores with precision. These predictions provide valuable insights for fantasy basketball decisions, player evaluation, and team strategies. Whether drafting or analyzing game performance, our data-driven predictions give you a competitive edge.

```{r echo=FALSE}
# Function to evaluate models and make fantasy decisions
make_fantasy_decisions_by_model <- function(predictions, test_data, thresholds, confidence_margin = 0.1) {
  # Create an empty list to store results by player
  results_by_player <- list()

  # Loop over each player to make predictions
  for (i in 1:nrow(test_data)) {
    player_name <- test_data$namePlayer[i]

    # Initialize variables to track the best prediction for the player
    best_prediction <- -Inf
    best_model <- NULL
    best_threshold <- NULL
    best_decision <- NULL
    all_predictions <- list()  # To store all predictions for this player

    # Loop over each model to evaluate the prediction for the current player
    for (model_name in names(predictions)) {
      prediction <- predictions[[model_name]][i]
      threshold <- thresholds[[model_name]]

      # Decision based on prediction above or below threshold and margin
      decision <- ifelse(prediction > threshold * (1 + confidence_margin), "Above Threshold", "Below Threshold")

      # Track the best prediction across models for the player
      if (prediction > best_prediction) {
        best_prediction <- prediction
        best_model <- model_name
        best_threshold <- threshold
        best_decision <- decision
      }

      # Store all predictions for this player
      all_predictions[[model_name]] <- list(
        model = model_name,
        prediction = round(prediction, 2),
        threshold = threshold,
        decision = decision
      )
    }

    # Store the best prediction and all predictions for the current player
    results_by_player[[player_name]] <- list(
      player_name = player_name,
      best_prediction = round(best_prediction, 2),
      best_model = best_model,
      best_threshold = best_threshold,
      best_decision = best_decision,
      all_predictions = all_predictions
    )
  }

  # Print the best prediction for each player along with all predictions
  for (player_name in names(results_by_player)) {
    result <- results_by_player[[player_name]]
    cat("\nPlayer:", result$player_name,
        "| Best Prediction:", result$best_prediction,
        "| Model:", result$best_model,
        "| Threshold:", result$best_threshold,
        "| Decision:", result$best_decision, "\n")

    cat("  All Predictions:\n")
    # Print all predictions for the player
    for (prediction in result$all_predictions) {
      cat("    Model:", prediction$model,
          "| Prediction:", prediction$prediction,
          "| Threshold:", prediction$threshold,
          "| Decision:", prediction$decision, "\n")
    }
  }
}

# Define the threshold for each model
thresholds <- list(
  points_model = 20,
  rebounds_model = 10,
  assists_model = 5,
  total_pra_model = 30,
  threepm_model = 2,
  stl_blk_model = 3,
  turnovers_model = 3,
  fantasy_score_model = 40
)

# Make fantasy decisions based on the predictions
make_fantasy_decisions_by_model(predictions, test_data, thresholds)

# Write the predictions to a text file
writeLines(capture.output(make_fantasy_decisions_by_model(predictions, test_data, thresholds)), "predictions.txt")
```
